---
title: "Untitled"
author: "yitong wang"
date: "4/7/2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("randomForest")
library(speff2trial)
library(tidyverse)
library(glmnet)
library(vcdExtra)
library(tidyverse)
library(manipulate)
library(caret)
library(sandwich)
library(lmtest)
library(boot)
library(pROC)
library(vars)
library(car)
library(Amelia)
library(randomForest)
library(knitr)
library(psych)
speff2trial::ACTG175
?ACTG175
#ACTG175$zprior
datan <- ACTG175
datan$zprior <- NULL
original_names <- colnames(datan)
```


#Single Munipulation
```{r}
set.seed(123)
a.out <- amelia(datan, m = 1, parallel = "multicore")

dat <- data.frame(a.out$imputations)
colnames(dat) <- original_names

#dat <- ACTG175[complete.cases(ACTG175),]
#a <- ACTG175$preanti
#str(a)
#length(a)
#sum(a)/length(a)

data <- dat
a <- (dat$cd420-dat$cd40)/dat$cd40
data$Y <- as.factor(ifelse(a >= 0.5, 1, 0))
data1 <-data

# Mannually TABLE 1
nrow(data1)
length(data1$str2[data1$str2==0])
length(data1$str2[data1$str2==1])
mean(data1$age)
sd(data1$age)
mean(data1$wtkg)
sd(data1$wtkg)
length(data1$gender[data1$gender==1])
length(data1$gender[data1$gender==1])*100 /2139

length(data1$race[data1$race==0])
length(data1$race[data1$race==0])*100 /2139

length(data1$race[data1$race==1])
length(data1$race[data1$race==1])*100 /2139

length(data1$homo[data1$homo==1]) #1=yes
length(data1$homo[data1$homo==1])*100 /2139

length(data1$drugs[data1$drugs==1]) #1=yes
length(data1$drugs[data1$drugs==1])*100 /2139

length(data1$hemo[data1$hemo==1]) #1=yes
length(data1$hemo[data1$hemo==1])*100 /2139

length(data1$karnof[data1$karnof==100]) #1=yes
length(data1$karnof[data1$karnof==100])*100 /2139

length(data1$symptom[data1$symptom==1]) #1=yes
length(data1$symptom[data1$symptom==1])*100 /2139

length(data1$z30[data1$z30==1]) #1=yes
length(data1$z30[data1$z30==1])*100 /2139

mean(data1$preanti)
sd(data1$preanti)

length(data1$oprior[data1$oprior==1]) #non-zidovudine antiretroviral therapy
length(data1$oprior[data1$oprior==1])*100 /2139

length(data1$gender[data1$gender==1 & data1$str2==0]) # 1=male
length(data1$gender[data1$gender==1& data1$str2==0])*100 /886
length(data1$gender[data1$gender==1 & data1$str2==1]) 
length(data1$gender[data1$gender==1& data1$str2==1])*100 /1253

length(data1$race[data1$race==0& data1$str2==0]) # 0=white
length(data1$race[data1$race==0& data1$str2==0])*100 /886
length(data1$race[data1$race==0& data1$str2==1]) 
length(data1$race[data1$race==0& data1$str2==1])*100 /1253

length(data1$race[data1$race==1& data1$str2==0])  # 1=non-white
length(data1$race[data1$race==1& data1$str2==0])*100 /886
length(data1$race[data1$race==1& data1$str2==1]) 
length(data1$race[data1$race==1& data1$str2==1])*100 /1253

length(data1$homo[data1$homo==1& data1$str2==0]) #1=yes
length(data1$homo[data1$homo==1 & data1$str2==0])*100 /886
length(data1$homo[data1$homo==1& data1$str2==1]) #1=yes
length(data1$homo[data1$homo==1 & data1$str2==1])*100 /1253

length(data1$drugs[data1$drugs==1& data1$str2==0]) #1=yes
length(data1$drugs[data1$drugs==1& data1$str2==0])*100 /886
length(data1$drugs[data1$drugs==1& data1$str2==1]) #1=yes
length(data1$drugs[data1$drugs==1& data1$str2==1])*100 /1253

length(data1$hemo[data1$hemo==1& data1$str2==0]) #1=yes
length(data1$hemo[data1$hemo==1& data1$str2==0])*100 /886
length(data1$hemo[data1$hemo==1& data1$str2==1]) #1=yes
length(data1$hemo[data1$hemo==1& data1$str2==1])*100 /1253

length(data1$karnof[data1$karnof==100& data1$str2==0])
length(data1$karnof[data1$karnof==100& data1$str2==0])*100 /886
length(data1$karnof[data1$karnof==100& data1$str2==1])
length(data1$karnof[data1$karnof==100& data1$str2==1])*100 /1253

length(data1$symptom[data1$symptom==1& data1$str2==0])
length(data1$symptom[data1$symptom==1& data1$str2==0])*100 /886
length(data1$symptom[data1$symptom==1& data1$str2==1])
length(data1$symptom[data1$symptom==1& data1$str2==1])*100 /1253

length(data1$z30[data1$z30==1 & data1$str2==0])
length(data1$z30[data1$z30==1 & data1$str2==0]) /886
length(data1$z30[data1$z30==1 & data1$str2==1])
length(data1$z30[data1$z30==1 & data1$str2==1]) /1253

length(data1$strat[data1$strat==3 & data1$str2==0]) #0=naive
length(data1$strat[data1$strat==3 & data1$str2==0]) /886
length(data1$strat[data1$strat==1 & data1$str2==1])
length(data1$strat[data1$strat==1 & data1$str2==1]) /1253

length(data1$oprior[data1$oprior==1 & data1$str2==0]) # 1=male
length(data1$oprior[data1$oprior==1& data1$str2==0])*100 /886
length(data1$oprior[data1$oprior==1 & data1$str2==1]) 
length(data1$oprior[data1$oprior==1& data1$str2==1])*100 /1253

# continuous variables

mean(data1$age[data1$gender==1])

baselineByGroup<- describeBy(data1,data1$str2,mat=TRUE)
baselineByGroup <- baselineByGroup[,c(-12,-13,-14,-15,-16,-17,-18,-19,-8,-9)]
str(baselineByGroup)
NO_PRIOR <- baselineByGroup[baselineByGroup$group1==0, ]
NO_PRIOR
PRIOR <- baselineByGroup[baselineByGroup$group1==1, ]
PRIOR
```


##Question2

###Data Munipulation by removing unrelated variables and spliting data into training and validation data
```{r}
data <- dat
a <- (dat$cd420-dat$cd40)/dat$cd40
data$Y <- as.factor(ifelse(a >= 0.5, 1, 0))
data1 <-data

#remove unrelated variables
#min(data1$zprior)
data1$pidnum <- NULL
data1$cd40 <- NULL
data1$cd420 <- NULL
data1$cd496 <- NULL
data1$r <- NULL
data1$offtrt <- NULL
data1$cd80 <- NULL
data1$cd820 <- NULL
data1$zprior <- NULL
data1$cens <- NULL
data1$days <- NULL
data1$treat <- NULL
data1$strat <- NULL

#factorize the indicators
data1$hemo <- factor(data1$hemo)
data1$homo <- factor(data1$homo)
data1$drugs <- factor(data1$drugs)
data1$oprior <- factor(data1$oprior)
data1$z30 <- factor(data1$z30)
data1$race <- factor(data1$race)
data1$gender <- factor(data1$gender)
data1$str2 <- factor(data1$str2)
#data1$strat <- factor(data1$strat)
data1$symptom <- factor(data1$symptom)
data1$arms <- factor(data1$arms)

#setting up the reference level
data1$hemo <- relevel(data1$hemo, ref = "0")
data1$homo <- relevel(data1$homo, ref = "0")
data1$drugs <- relevel(data1$drugs, ref = "0")
data1$oprior <- relevel(data1$oprior, ref = "0")
data1$z30 <- relevel(data1$z30, ref = "0")
data1$race <- relevel(data1$race, ref = "0")
data1$gender <- relevel(data1$gender, ref = "0")
data1$str2 <- relevel(data1$str2, ref = "0")
#data1$strat <- relevel(data1$strat, ref = "1")
data1$symptom <- relevel(data1$symptom, ref = "0")
data1$arms <- relevel(data1$arms, ref = "0")

#length(data1)

#spliting data into validation and training data
n<-nrow(data1)
set.seed(123)
train<- sample(n, n*0.6)
data1train<- data1[train,]
data1test<- data1[-train,]

#data <- data.frame(matrix(rnorm(9 * 10), ncol = 9))
#names(data) <- c(paste0("x", 1:8), "y")
# First step: using .*. for all interactions
#f <- as.formula(y ~ .*.)
#y <- data$y
# Second step: using model.matrix to take advantage of f
#x <- model.matrix(f, data)[, -1]
```



###model selection by checking out-of-sample AUC
```{r}

fit1<- glm(Y ~ . , data=data1train, family=binomial)
fit2<- glm(Y ~ .+age*karnof , data=data1train, family=binomial)
fit3<- glm(Y ~ .+wtkg*homo , data=data1train, family=binomial)
fit4<- glm(Y ~ .+hemo*arms , data=data1train, family=binomial)
fit5<- glm(Y ~ .+homo*arms, data=data1train, family=binomial)
fit6<- glm(Y ~ .+race*arms , data=data1train, family=binomial)
fit7<- glm(Y ~ .+race*symptom , data=data1train, family=binomial)
fit8<- glm(Y ~ .+gender*symptom , data=data1train, family=binomial)
fit9<- glm(Y ~ .+arms*symptom , data=data1train, family=binomial)
fit10<- glm(Y ~ .+arms*wtkg , data=data1train, family=binomial)
fit11<- glm(Y ~ .+arms*drugs , data=data1train, family=binomial)##winner!!

#alias(fit1)
summary(fit1)
summary(fit2)
summary(fit3)
summary(fit4)
summary(fit5)
summary(fit6)
summary(fit7)
summary(fit8)
summary(fit9)

#AUC
pred1test <- predict(fit1, newdata = data1test, type = 'response')
pred2test <- predict(fit2, newdata = data1test, type = 'response')
pred3test <- predict(fit3, newdata = data1test, type = 'response')
pred4test <- predict(fit4, newdata = data1test, type = 'response')
pred5test <- predict(fit5, newdata = data1test, type = 'response')
pred6test <- predict(fit6, newdata = data1test, type = 'response')
pred7test <- predict(fit7, newdata = data1test, type = 'response')
pred8test <- predict(fit8, newdata = data1test, type = 'response')
pred9test <- predict(fit9, newdata = data1test, type = 'response')
pred10test <- predict(fit10, newdata = data1test, type = 'response')
pred11test <- predict(fit11, newdata = data1test, type = 'response')
#as.numeric(ctest$Y)* log(pred1test)

roc1t<-roc(data1test$Y~pred1test)
roc2t<-roc(data1test$Y~pred2test)
roc3t<-roc(data1test$Y~pred3test) 
roc4t<-roc(data1test$Y~pred4test)
roc5t<-roc(data1test$Y~pred5test) 
roc6t<-roc(data1test$Y~pred6test)
roc7t<-roc(data1test$Y~pred7test)
roc8t<-roc(data1test$Y~pred8test)
roc9t<-roc(data1test$Y~pred9test) 
roc10t<-roc(data1test$Y~pred10test)
roc11t<-roc(data1test$Y~pred11test)

group_compare <-rbind(roc1t$auc,roc2t$auc,roc3t$auc,roc4t$auc,roc5t$auc,roc6t$auc,roc7t$auc,roc8t$auc,roc9t$auc,roc10t$auc,roc11t$auc)

group_compare <- data.frame(group_compare)

rownames(group_compare) <- c("model1", "model2", "model3", "model4", "model5", "model6", "model7", "model8", "model9", "model10", "model11")

colnames(group_compare) <- "AUC"

knitr::kable(group_compare)
  
```

###model selection by using lasso
```{r}
library(glmnet)

datan <- as.matrix(data1train)

train.x<- model.matrix(~., data = data1train[,1:14])
train.y<- as.numeric(datan[,15])

#f <- as.formula(y ~ .*.)

#train.x <- model.matrix(f, data1train)[,-1]
#datat <- as.matrix(data1test)

test.x <- model.matrix(~., data = data1test[,1:14])


cvfit = cv.glmnet(train.x, train.y, family="binomial", type.measure = "auc")
pred.y = predict(cvfit, test.x, type = "response", s="lambda.1se")

#cvfit$lambda
#c(cvfit$lambda.min, cvfit$lambda.1se)
#predict(cvfit, newx=x[1:5,], type="response", s="lambda.1se")
n <- which(cvfit$lambda == cvfit$lambda.min)

coef(cvfit, s=c(cvfit$lambda[n],0.1))

roct<-roc(data1test$Y~pred.y)
roct
plot(roct, print.thres=TRUE,print.auc=TRUE, col=1, main="ROC of model 1 test")
```

###model selection by using stepwise AUC
```{r}
stepAIC(glm(Y ~ (.)^2, data=data1train, family=binomial))
#fit<- glm(Y ~ age + wtkg + hemo + drugs + karnof + oprior + z30 + preanti + race + gender + arms , data=ctrain, family=binomial)


fit <- glm(formula = Y ~ age + wtkg + hemo + homo + drugs + karnof + 
    oprior + z30 + preanti + race + gender + str2 + symptom + 
    arms + age:drugs + age:symptom + hemo:z30 + homo:z30 + homo:str2 + 
    homo:arms + drugs:z30 + drugs:str2 + karnof:symptom + oprior:z30 + 
    oprior:race + z30:race + preanti:str2 + race:gender + race:str2 + 
    race:arms + gender:symptom + str2:symptom + str2:arms + symptom:arms, 
    family = binomial, data = data1train)


predtest <- predict(fit, newdata = data1test, type = 'response')
roct<-roc(data1test$Y~predtest)
roct
plot(roct, print.thres=TRUE,print.auc=TRUE, col=1, main="ROC of model 1 test")
```

###model selection by using random forest
```{r}
a <- randomForest(train.x[,-1], factor(train.y))
predtest <- predict(a, newdata = model.matrix(~.,data1test)[,-1], type = 'prob')
#nrow(predtest)
#length(predtest)
#length(model.matrix(~.,data1test)[,15])
#nrow(model.matrix(~.,data1test))
#data1test$Y
#model.matrix(~.,data1test)
roct<-roc(factor(data1test$Y)~predtest[,2])
roct$auc
plot(roct, print.thres=TRUE,print.auc=TRUE, col=1, main="ROC of model 1 test")

#importance(a)
#rfcv(train.x, train.y)
```



###multivariate&conditional odds ratio
```{r}
#fit1<- glm(Y ~ ., data=data1train, family=binomial)

#fit1<- glm(Y ~ (.)^2, data=data1train, family=binomial)

#fit1<- glm(Y ~ . + str2:z30, data=data1train, family=binomial)

fit2<- glm(Y ~ . + arms:drugs, data=data1train, family=binomial) ## selected model

#fit1<- glm(Y ~ . + homo:gender, data=data1train, family=binomial)

#fit1<- glm(Y ~ . + oprior:arms, data=data1train, family=binomial)


#summary(fit2)

#coef(fit2)

a <- summary(fit2, corr=T)

#coef(fit2)

age <- exp(coef(fit2)[2])

wtkg <- exp(coef(fit2)[3])

hemo <- exp(coef(fit2)[4])

homo <- exp(coef(fit2)[5])

#drugs <- exp(coef(fit2)[6])###interaction

karnof <- exp(coef(fit2)[7])

oprior <- exp(coef(fit2)[8])

z30 <- exp(coef(fit2)[9])

preanti <- exp(coef(fit2)[10])

race <- exp(coef(fit2)[11])

gender <- exp(coef(fit2)[12])

str2 <- exp(coef(fit2)[13])

symptom <- exp(coef(fit2)[14])


odds_fit <- rbind(age, wtkg, hemo, homo, karnof, oprior, z30, preanti, race, gender, str2, symptom)

colnames(odds_fit) <- "Conditional Odds Ratio"

knitr::kable(odds_fit)

```



###ROC Curve for the selected model
```{r}
pred1train <- predict(fit1, newdata = data1train, type = 'response')
pred1test <- predict(fit1, newdata = data1test, type = 'response')

CE_train1 <- -(mean(as.numeric(data1train$Y) * log(pred1train) + (1-as.numeric(data1train$Y)) * log(1 - pred1train)))

CE_test1 <- -(mean(as.numeric(data1test$Y) * log(pred1test) + (1-as.numeric(data1test$Y)) * log(1 - pred1test)))

cross_entropy <- c(CE_train1, CE_test1)
cross_entropy

roc1train<-roc(data1train$Y~pred1train)
roc1test<-roc(data1test$Y~pred1test)

auc_train1 <- roc1train$auc
auc_test1 <- roc1test$auc

auc <- cbind(auc_train1, auc_test1)
auc

#plot(roc1train,print.thres=TRUE, print.auc=TRUE, col=3, main="ROC of model 2 train ")

plot(roc1test, print.thres=TRUE,print.auc=TRUE, col=1, main="ROC of model 1 test")

```

##Question3
```{r}
library(boot)

dat1 <-ACTG175 %>%
  filter(arms == 1)

n2 <- nrow(dat1)

dat2 <-ACTG175 %>%
  filter(arms == 0)

n1 <- nrow(dat2)

a <- (dat1$cd496-dat1$cd40)/dat1$cd40
dat1$Y <- as.factor(ifelse(a >= 0.5, 1, 0))

b <- (dat2$cd496-dat2$cd40)/dat2$cd40
dat2$Y <- as.factor(ifelse(b >= 0.5, 1, 0))

end496_2 <- sum(na.omit(dat1$Y==1))

end496_1 <- sum(na.omit(dat2$Y==1))

ate <- (sum(na.omit(dat1$Y==1))/length(na.omit(dat1$Y))) - (sum(na.omit(dat2$Y==1))/length(na.omit(dat2$Y)))
ate


a1 <- (dat1$cd420-dat1$cd40)/dat1$cd40
dat1$Y1 <- as.factor(ifelse(a1 >= 0.5, 1, 0))

b1 <- (dat2$cd420-dat2$cd40)/dat2$cd40
dat2$Y1 <- as.factor(ifelse(b1 >= 0.5, 1, 0))

end420_2 <- sum(na.omit(dat1$Y1==1))

end420_1 <- sum(na.omit(dat2$Y1==1))

ate1 <- (end420_2/length(na.omit(dat1$Y1))) - (end420_1/length(na.omit(dat2$Y1)))
ate1


datam <- ACTG175

am <- (datam$cd496-datam$cd40)/datam$cd40
datam$Y <- as.factor(ifelse(am >= 0.5, 1, 0))

an <- (datam$cd420-datam$cd40)/datam$cd40
datam$Y1 <- as.factor(ifelse(an >= 0.5, 1, 0))


ATE <- function(data, indices){
  d <- data[indices,]
  
    dat1 <-d %>%
      filter(arms == 1)
    
    dat2 <-d %>%
      filter(arms == 0)

    ate <- (sum(na.omit(dat1$Y==1))/length(na.omit(dat1$Y))) - (sum(na.omit(dat2$Y==1))/length(na.omit(dat2$Y)))
    
    ate1 <- (sum(na.omit(dat1$Y1==1))/length(na.omit(dat1$Y1))) - (sum(na.omit(dat2$Y1==1))/length(na.omit(dat2$Y1)))
  
  return(c(ate, ate1))
}

boot_ate <- boot(data = datam, statistic= ATE, R = 100)

boot_ate

se1 <- sd(boot_ate$t[,1])

lower1 <- ate-1.96*se1
upper1 <- ate + 1.96*se1

se2 <- sd(boot_ate$t[,2])

lower2 <- ate1-1.96*se2
upper2 <- ate1 + 1.96*se2

n <- cbind(n1, n2)

week20 <- cbind(end420_1, end420_2)

week96 <- cbind(end496_1, end496_2)

tableate <- rbind(n, week20, week96)

colnames(tableate) <- c("Zidovudine", "Zidovudine and Didanosine")

rownames(tableate) <- c("Total", "20 Weeks", "96 Weeks")

ates <- cbind(ate, lower1, upper1)
ates1 <- cbind(ate1, lower2, upper2)

allate <- rbind(ates1, ates)

rownames(allate) <- c("20 Weeks", "96 Weeks")

colnames(allate) <- c("ATE", "lower CI", "upper CI")

knitr::kable(allate)

knitr::kable(tableate)

#n<-nrow(data1)
#set.seed(123)
#train<- sample(n, n*0.6)
#data1train<- data1[train,]
#data1test<- data1[-train,]
```

##Question4

###Data Munipulation
```{r}
data1 <-dat

#remove unrelated variables
#min(data1$zprior)
data1$pidnum <- NULL
data1$cd420 <- NULL
data1$cd496 <- NULL
data1$r <- NULL
data1$cd80 <- NULL
data1$cd820 <- NULL
data1$zprior <- NULL
data1$cens <- NULL
data1$days <- NULL
data1$treat <- NULL
data1$strat <- NULL

data1$hemo <- factor(data1$hemo)
data1$homo <- factor(data1$homo)
data1$drugs <- factor(data1$drugs)
data1$oprior <- factor(data1$oprior)
data1$z30 <- factor(data1$z30)
data1$race <- factor(data1$race)
data1$gender <- factor(data1$gender)
data1$str2 <- factor(data1$str2)
#data1$strat <- factor(data1$strat)
data1$symptom <- factor(data1$symptom)
data1$arms <- factor(data1$arms)
data1$offtrt <- factor(data1$offtrt)
str(data1)

data1$hemo <- relevel(data1$hemo, ref = "0")
data1$homo <- relevel(data1$homo, ref = "0")
data1$drugs <- relevel(data1$drugs, ref = "0")
data1$oprior <- relevel(data1$oprior, ref = "0")
data1$z30 <- relevel(data1$z30, ref = "0")
data1$race <- relevel(data1$race, ref = "0")
data1$gender <- relevel(data1$gender, ref = "0")
data1$str2 <- relevel(data1$str2, ref = "0")
#data1$strat <- relevel(data1$strat, ref = "1")
data1$symptom <- relevel(data1$symptom, ref = "0")
data1$arms <- relevel(data1$arms, ref = "0")
data1$offtrt <- relevel(data1$offtrt, ref = "0")

length(data1)

n<-nrow(data1)
set.seed(123)
train<- sample(n, n*0.6)
data1train<- data1[train,]
data1test<- data1[-train,]
```

###model selection by using lasso
```{r}
library(glmnet)

datan <- as.matrix(data1train)

data1train1 <- data1train
data1train1$offtrt <- NULL

train.x<- model.matrix(~., data = data1train1)
train.y<- as.numeric(datan[,14])

#f <- as.formula(y ~ .*.)

#train.x <- model.matrix(f, data1train)[,-1]
#datat <- as.matrix(data1test)
#data1test$offtrt <- NULL

test.x <- model.matrix(~., data = data1test)


cvfit = cv.glmnet(train.x, train.y, family="binomial", type.measure = "auc")
pred.y = predict(cvfit, test.x, type = "response", s="lambda.1se")

#cvfit$lambda
#c(cvfit$lambda.min, cvfit$lambda.1se)
#predict(cvfit, newx=x[1:5,], type="response", s="lambda.1se")
n <- which(cvfit$lambda == cvfit$lambda.min)

coef(cvfit, s=c(cvfit$lambda[n],0.1))

roct<-roc(data1test$offtrt~pred.y)
roct
plot(roct, print.thres=TRUE,print.auc=TRUE, col=1, main="ROC of model 1 test")
```

###model selection by out-of-sample AUC
```{r}
fit1<- glm(offtrt ~. , data=data1train, family=binomial)
fit2<- glm(offtrt ~. + wtkg*arms, data=data1train, family=binomial)#winner!!!!
fit3<- glm(offtrt ~. + str2:z30, data=data1train, family=binomial)
fit5<- glm(offtrt ~. + homo:gender, data=data1train, family=binomial)
fit6<- glm(offtrt ~. + homo:hemo, data=data1train, family=binomial)
fit7<- glm(offtrt ~. + oprior:drugs, data=data1train, family=binomial)
fit8<- glm(offtrt ~. + hemo:gender, data=data1train, family=binomial)
fit9<- glm(offtrt ~. + homo:drugs, data=data1train, family=binomial)
fit10<- glm(offtrt ~. + str2:oprior, data=data1train, family=binomial)

summary(fit2)

#AUC
pred1test <- predict(fit1, newdata = data1test, type = 'response')
pred2test <- predict(fit2, newdata = data1test, type = 'response')
pred3test <- predict(fit3, newdata = data1test, type = 'response')
pred4test <- predict(fit4, newdata = data1test, type = 'response')
pred5test <- predict(fit5, newdata = data1test, type = 'response')
pred6test <- predict(fit6, newdata = data1test, type = 'response')
pred7test <- predict(fit7, newdata = data1test, type = 'response')
pred8test <- predict(fit8, newdata = data1test, type = 'response')
pred9test <- predict(fit9, newdata = data1test, type = 'response')
pred10test <- predict(fit10, newdata = data1test, type = 'response')
#pred11test <- predict(fit11, newdata = ctest, type = 'response')
#as.numeric(ctest$Y)* log(pred1test)

roc1t<-roc(data1test$offtrt~pred1test)
roc2t<-roc(data1test$offtrt~pred2test)
roc3t<-roc(data1test$offtrt~pred3test) 
roc4t<-roc(data1test$offtrt~pred4test)
roc5t<-roc(data1test$offtrt~pred5test) 
roc6t<-roc(data1test$offtrt~pred6test)
roc7t<-roc(data1test$offtrt~pred7test)
roc8t<-roc(data1test$offtrt~pred8test)
roc9t<-roc(data1test$offtrt~pred9test) 
roc10t<-roc(data1test$offtrt~pred10test)
#roc11t<-roc(data1test$Y~pred11test)

group_compare <-rbind(roc1t$auc,roc2t$auc,roc3t$auc,roc4t$auc,roc5t$auc,roc6t$auc,roc7t$auc,roc8t$auc,roc9t$auc,roc10t$auc)

group_compare <- data.frame(group_compare)

rownames(group_compare) <- c("model1", "model2", "model3", "model4", "model5", "model6", "model7", "model8", "model9", "model10")

colnames(group_compare) <- "AUC"

knitr::kable(group_compare)

a <- summary(fit2, corr=T)
```
###model selection by using stepwise AUC
```{r}
stepAIC(glm(offtrt ~ (.)^2, data=data1train, family=binomial))
#fit<- glm(Y ~ age + wtkg + hemo + drugs + karnof + oprior + z30 + preanti + race + gender + arms , data=ctrain, family=binomial)


fit <- glm(formula = offtrt ~ age + wtkg + hemo + homo + drugs + karnof + 
    oprior + z30 + preanti + race + gender + str2 + symptom + 
    cd40 + arms + age:oprior + age:gender + wtkg:karnof + wtkg:oprior + 
    wtkg:cd40 + hemo:drugs + hemo:karnof + hemo:oprior + hemo:race + 
    homo:karnof + homo:race + drugs:oprior + oprior:z30 + oprior:preanti + 
    oprior:race + oprior:symptom + oprior:cd40 + oprior:arms + 
    z30:symptom + preanti:str2 + gender:cd40 + str2:cd40 + symptom:arms, 
    family = binomial, data = data1train)



predtest <- predict(fit, newdata = data1test, type = 'response')
roct<-roc(data1test$offtrt~predtest)
roct
plot(roct, print.thres=TRUE,print.auc=TRUE, col=1, main="ROC of model 1 test")
```



###model selection by using random forest
```{r}
a <- randomForest(train.x[,-1], factor(train.y))
predtest <- predict(a, newdata = model.matrix(~.,data1test)[,-1], type = 'prob')
#nrow(predtest)
#length(predtest)
#length(model.matrix(~.,data1test)[,15])
#nrow(model.matrix(~.,data1test))
#data1test$Y
#model.matrix(~.,data1test)
roct<-roc(factor(data1test$offtrt)~predtest[,2])
roct$auc
plot(roct, print.thres=TRUE,print.auc=TRUE, col=1, main="ROC of model 1 test")

#importance(a)
#rfcv(train.x, train.y)
```


###ROC Curve for the final model
```{r}
fit2<- glm(offtrt ~. + wtkg*arms, data=data1train, family=binomial)#winner!!!!

pred2train <- predict(fit2, newdata = data1train, type = 'response')
pred2test <- predict(fit2, newdata = data1test, type = 'response')

CE_train2 <- -(mean(as.numeric(data1train$offtrt) * log(pred2train) + (1-as.numeric(data1train$offtrt)) * log(1 - pred2train)))

CE_test2 <- -(mean(as.numeric(data1test$offtrt) * log(pred2test) + (1-as.numeric(data1test$offtrt)) * log(1 - pred2test)))

cross_entropy2 <- c(CE_train2, CE_test2)
cross_entropy2

roc2train<-roc(data1train$offtrt~pred2train)
roc2test<-roc(data1test$offtrt~pred2test)

auc_train2 <- roc2train$auc
auc_test2 <- roc2test$auc

auc2 <- cbind(auc_train2, auc_test2)
auc2

#plot(roc2train,print.thres=TRUE, print.auc=TRUE, col=3, main="ROC of model 2 train ")

plot(roc2test, print.thres=TRUE,print.auc=TRUE, col=1, main="ROC of model 1 test")
```

#marginal risk ratio 
```{r}
# marginal risk ratio 
fit2<- glm(offtrt ~. + wtkg*arms, data=data1, family=binomial)#winner 0.625

  bd0<- data1
  bd0$str2 <- ifelse(as.numeric(as.character(bd0$str2)) == 1, 0, as.numeric(as.character(bd0$str2)))
  bd0$str2 <- as.factor(bd0$str2)
  
  bd1 <- data1
  bd1$str2 <- ifelse(as.numeric(as.character(bd1$str2)) == 0, 1, as.numeric(as.character(bd1$str2)))
  bd1$str2 <- as.factor(bd1$str2)

pb1 <- predict(fit2, newdata = bd1, type = 'response')
pb0 <- predict(fit2, newdata = bd0, type = 'response')
rr <- mean(pb1)/mean(pb0)

# 95% confidence interval for rr 
set.seed(123)
logit.bootstrap_rr <- function(formula, data, indices) {
  
  d <- data[indices, ]
  fit1 <- glm(formula, data = d, family = 'binomial')
  
  bd0<- d
  bd0$str2 <- ifelse(as.numeric(as.character(bd0$str2)) == 1, 0, as.numeric(as.character(bd0$str2)))
  bd0$str2 <- as.factor(bd0$str2)
  
  bd1 <- d
  bd1$str2 <- ifelse(as.numeric(as.character(bd1$str2)) == 0, 1, as.numeric(as.character(bd1$str2)))
  bd1$str2 <- as.factor(bd1$str2)

  ## marginal odds ratio on ldl increase
  pred<- predict(fit1, newdata = bd0, type = 'response')
  add1 <- predict(fit1, newdata = bd1, type = 'response')
  
  RR1 <- mean(add1) / mean(pred)
  

  
  #pb1 <- predict(fit, newdata = bd1, type = 'response')
  #pb0 <- predict(fit, newdata = bd0, type = 'response')
  #rr <- mean(pb1)/mean(pb0)
  return(RR1)
}

rr_ci <- boot(data=data1, statistic=logit.bootstrap_rr, R=100, formula=offtrt ~. + wtkg*arms)
rr_ci
#rr_ci$t
rr
se1 <- sd(rr_ci$t)

c(rr-1.96*se1, rr + 1.96*se1)


```

